---
title: "YEP SUD"
output: html_document
date: "2023-02-09"
---

```{r setup, include = FALSE}
setwd("C:/Users/Work/Documents/YEP SUD Manuscript")
library(tidyverse)
library(haven)

demographics <- read_sav("demographics both sites all cohorts.sav")
sud <- read_sav("Substance Abuse_All Cohorts_Both Sites_T1.sav")
lsi <- read_sav("Chronic LSI Time 1_All cohorts_ both sites.sav")
SCIDs <- read_sav("SCID Consensus All Times-Both sites_ All cohorts.sav")


#loading all the files
files <- c("SUD T1.sav", "SUD T3.sav", "SUD T5.sav", "SUD T7.sav",
           "SUD T9.sav", "SUD T11.sav", "SUD T13.sav", "SUD T15.sav",
           "SUD T17.sav", "SUD T19.sav")
for (f in files){
  df <- read_sav(f)
  assign(gsub(".sav", "", f), df)
}

#lsi is broken into subscales
#allison's paper used three models: total, interpersonal, and non-interpersonal
#total was created by averaging across all relevant domains

#clean the lsi first
#create a total by averaging across all items
lsi <- lsi %>% 
  select(!(contains("specifier"))) %>%
  rowwise() %>%
  mutate(tot_avg = mean(c_across(lsi_friendship_t1:lsi_family_health_t1))) %>%
  mutate(int_avg = mean(c_across(c(lsi_friendship_t1, lsi_romantic_t1,
                                   lsi_social_t1, lsi_family_t1)))) %>%
  mutate(nonint_avg = mean(c_across(c(lsi_neighborhood_t1, lsi_school_t1,
                                      lsi_work_t1, lsi_finances_t1, 
                                      lsi_self_health_t1, lsi_family_health_t1))))
#numbers of averages line up with allison's paper
```

ALCOHOL ABUSE CSRs at t1
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t1)
test
```

t5 (because no t3)
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t5)
test
```

t7
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t7)
test
```

t9
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t9)
test
```


t11 (this is a capital T)
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_T11)
test
```

t13
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t13)
test
```

t15
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t15)
test
```

t17
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t17)
test
```

t19
```{r}
test <- SCIDs %>% select(contains("alab_cur_csr")) %>%
  count(alab_cur_csr_t19)
test
```



ALCOHOL DEPENDENCE CSRs at t1
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t1)
test
```

t5 (because no t3)
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t5)
test
```

t7
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t7)
test
```

t9
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t9)
test
```


t11 (this is a capital T)
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_T11)
test
```

t13
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t13)
test
```

t15
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t15)
test
```

t17
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t17)
test
```

t19
```{r}
test <- SCIDs %>% select(contains("aldep_cur_csr")) %>%
  count(aldep_cur_csr_t19)
test
```



what if we pare the sample down to anyone who was EVER given a CSR for alcohol abuse at ANY time point, there are:
```{r, echo = FALSE}
test <- SCIDs %>% filter(alab_cur_csr_t1 != 0 &
                           !is.na(alab_cur_csr_t1) |
                           alab_cur_csr_t5 != 0 & 
                           !is.na(alab_cur_csr_t5) |
                           alab_cur_csr_t7 != 0 &
                           !is.na(alab_cur_csr_t7) |
                           alab_cur_csr_t9 != 0 &
                           !is.na(alab_cur_csr_t9) |
                           alab_cur_csr_T11 != 0 &
                           !is.na(alab_cur_csr_T11) |
                           alab_cur_csr_t13 != 0 &
                           !is.na(alab_cur_csr_t13) |
                           alab_cur_csr_t15 != 0 &
                           !is.na(alab_cur_csr_t15) |
                           alab_cur_csr_t17 != 0 &
                           !is.na(alab_cur_csr_t17) |
                           alab_cur_csr_t19 != 0 &
                           !is.na(alab_cur_csr_t19)) %>%
  select(alab_cur_csr_t1, alab_cur_csr_t5, alab_cur_csr_t7,
         alab_cur_csr_t9, alab_cur_csr_T11, alab_cur_csr_t13, 
         alab_cur_csr_t15, alab_cur_csr_t17, alab_cur_csr_t19)
nrow(test)
```
participants in this data set

how many people in this data set have CSRs above 4 at any time point?
```{r, echo = FALSE}
test <- SCIDs %>% filter(alab_cur_csr_t1 >= 4 |
                           alab_cur_csr_t5 >= 4|
                           alab_cur_csr_t7 >= 4|
                           alab_cur_csr_t9 >= 4|
                           alab_cur_csr_T11 >= 4|
                           alab_cur_csr_t13 >= 4|
                           alab_cur_csr_t15 >= 4|
                           alab_cur_csr_t17 >= 4|
                           alab_cur_csr_t19 >= 4) %>%
  select(alab_cur_csr_t1, alab_cur_csr_t5, alab_cur_csr_t7,
         alab_cur_csr_t9, alab_cur_csr_T11, alab_cur_csr_t13, 
         alab_cur_csr_t15, alab_cur_csr_t17, alab_cur_csr_t19)
nrow(test)
```


what if we pare the sample down to anyone who was EVER given a CSR for alcohol dependence?
```{r, echo = FALSE}
test <- SCIDs %>% filter(aldep_cur_csr_t1 != 0 &
                           !is.na(aldep_cur_csr_t1) |
                           aldep_cur_csr_t5 != 0 & 
                           !is.na(aldep_cur_csr_t5) |
                           aldep_cur_csr_t7 != 0 &
                           !is.na(aldep_cur_csr_t7) |
                           aldep_cur_csr_t9 != 0 &
                           !is.na(aldep_cur_csr_t9) |
                           aldep_cur_csr_T11 != 0 &
                           !is.na(aldep_cur_csr_T11) |
                           aldep_cur_csr_t13 != 0 &
                           !is.na(aldep_cur_csr_t13) |
                           aldep_cur_csr_t15 != 0 &
                           !is.na(aldep_cur_csr_t15) |
                           aldep_cur_csr_t17 != 0 &
                           !is.na(aldep_cur_csr_t17) |
                           aldep_cur_csr_t19 != 0 &
                           !is.na(aldep_cur_csr_t19)) %>%
  select(aldep_cur_csr_t1, aldep_cur_csr_t5, aldep_cur_csr_t7,
         aldep_cur_csr_t9, aldep_cur_csr_T11, aldep_cur_csr_t13, 
         aldep_cur_csr_t15, aldep_cur_csr_t17, aldep_cur_csr_t19)
nrow(test)
```
now there are 125 participants

filtering to any who have CSR >= 4 at all for alc dependence
```{r, echo = FALSE}
test <- SCIDs %>% filter(aldep_cur_csr_t1 >= 4 |
                           aldep_cur_csr_t5 >= 4|
                           aldep_cur_csr_t7 >= 4|
                           aldep_cur_csr_t9 >= 4|
                           aldep_cur_csr_T11 >= 4|
                           aldep_cur_csr_t13 >= 4|
                           aldep_cur_csr_t15 >= 4|
                           aldep_cur_csr_t17 >= 4|
                           aldep_cur_csr_t19 >= 4) %>%
  select(aldep_cur_csr_t1, aldep_cur_csr_t5, aldep_cur_csr_t7,
         aldep_cur_csr_t9, aldep_cur_csr_T11, aldep_cur_csr_t13, 
         aldep_cur_csr_t15, aldep_cur_csr_t17, aldep_cur_csr_t19)
nrow(test)
```



table of alcohol abuse CSRs from all timepoints
```{r, echo = FALSE}

alabt1 <- SCIDs %>% count(alab_cur_csr_t1) %>%
  rename(CSR = alab_cur_csr_t1,
         alab_cur_csr_t1 = n)
alabt5 <- SCIDs %>% count(alab_cur_csr_t5) %>%
  rename(CSR = alab_cur_csr_t5,
         alab_cur_csr_t5 = n)
alabt7 <- SCIDs %>% count(alab_cur_csr_t7) %>%
  rename(CSR = alab_cur_csr_t7,
         alab_cur_csr_t7 = n)
alabt9 <- SCIDs %>% count(alab_cur_csr_t9) %>%
  rename(CSR = alab_cur_csr_t9,
         alab_cur_csr_t9 = n)
alabT11 <- SCIDs %>% count(alab_cur_csr_T11) %>%
  rename(CSR = alab_cur_csr_T11,
         alab_cur_csr_T11 = n)
alabt13 <- SCIDs %>% count(alab_cur_csr_t13) %>%
  rename(CSR = alab_cur_csr_t13,
         alab_cur_csr_t13 = n)
alabt15 <- SCIDs %>% count(alab_cur_csr_t15) %>%
  rename(CSR = alab_cur_csr_t15,
         alab_cur_csr_t15 = n)
alabt17 <- SCIDs %>% count(alab_cur_csr_t17) %>%
  rename(CSR = alab_cur_csr_t17,
         alab_cur_csr_t17 = n)
alabt19 <- SCIDs %>% count(alab_cur_csr_t19) %>% 
  rename(CSR = alab_cur_csr_t19,
         alab_cur_csr_t19 = n)


testList <- list(alabt1, alabt5, alabt7, alabt9, alabT11, alabt13,
                 alabt15, alabt17, alabt19)
testList <- testList %>% reduce(full_join, by = "CSR")
testList
```


table of all alc dependence CSRs from all timepoints
```{r, echo = FALSE}
aldept1 <- SCIDs %>% count(aldep_cur_csr_t1) %>%
  rename(CSR = aldep_cur_csr_t1,
         aldep_cur_csr_t1 = n)
aldept5 <- SCIDs %>% count(aldep_cur_csr_t5) %>%
  rename(CSR = aldep_cur_csr_t5,
         aldep_cur_csr_t5 = n)
aldept7 <- SCIDs %>% count(aldep_cur_csr_t7) %>%
  rename(CSR = aldep_cur_csr_t7,
         aldep_cur_csr_t7 = n)
aldept9 <- SCIDs %>% count(aldep_cur_csr_t9) %>%
  rename(CSR = aldep_cur_csr_t9,
         aldep_cur_csr_t9 = n)
aldepT11 <- SCIDs %>% count(aldep_cur_csr_T11) %>%
  rename(CSR = aldep_cur_csr_T11,
         aldep_cur_csr_T11 = n)
aldept13 <- SCIDs %>% count(aldep_cur_csr_t13) %>%
  rename(CSR = aldep_cur_csr_t13,
         aldep_cur_csr_t13 = n)
aldept15 <- SCIDs %>% count(aldep_cur_csr_t15) %>%
  rename(CSR = aldep_cur_csr_t15,
         aldep_cur_csr_t15 = n)
aldept17 <- SCIDs %>% count(aldep_cur_csr_t17) %>%
  rename(CSR = aldep_cur_csr_t17,
         aldep_cur_csr_t17 = n)
aldept19 <- SCIDs %>% count(aldep_cur_csr_t19) %>% 
  rename(CSR = aldep_cur_csr_t19,
         aldep_cur_csr_t19 = n)


testList <- list(aldept1, aldept5, aldept7, aldept9, aldepT11, aldept13,
                 aldept15, aldept17, aldept19)
testList <- testList %>% reduce(full_join, by = "CSR") 
testList
```